Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 PandaOverview.tex

PanDA's application model assumes tasks, workloads and workflows. Tasks
represent a set of operations performed on a set of events that are stored in
one or more input files. Tasks are decomposed into jobs, where each job
represents the task's set of operations and a partition of the task's events.
Since 2005, a certain amount of parallelism has been progressively introduced
for job execution~\cite{crooks2012multi} but, so far, no MPI jobs have been
considered for production. Jobs are supposed to be relatively self-contained,
capable of setting up their own execution environment or having a minimal set of
common dependences.

@@

Currently, PanDA's execution model is based on five main abstractions: task,
job, queue, pilot, and event. Both tasks and jobs are assumed to have attributes
and states and to be queued into a global queue for execution. Prioritization
and binding of jobs are assumed to depend on the attributes of each job. Pilot
is used to indicate the abstraction of resource capabilities. Each job is
thought to be bound to one pilot and executed on the site where the pilot has
been instantiated.

In PanDA's data model, each event refers to the recorded or simulated
measurement of a physical event. One or more events can be packaged into files
or other data containers. As with jobs, data have both attributes and states,
and some of the attributes are shared between events and jobs. Raw,
reconstruction, and simulation data are assumed to be distributed across
multiple storage facilities and managed by the ATLAS Distributed Data Management
(DDM)~\cite{garonne2012atlas}. When necessary, datasets required by each job are
assumed to be replicated over the network, both for input and output data.

@@

The implementation of PanDA consists of several interconnected subsystems, most
of them built from off-the-shelf and Open Source components. Subsystems
communicate via dedicated API or HTTP messaging, and each subsystem is
implemented by one or more modules. Databases are used to store eventful
entities like tasks, jobs and events, and to store information about sites,
resources, logs, and accounting.

>>>>

\mtnote{Addresses Alexei's comment. I eliminated `event' as abstraction and used
datum/data/physical process when discussing data management in the whole
section.}

PanDA's application model assumes tasks, workloads and workflows. Tasks
represent a set of operations performed on
% a set of events that are
data sets stored in one or more input files. Tasks are decomposed into jobs,
where each job represents the task's set of operations and a partition of the
task's
% events
data set. Since 2005, a certain amount of parallelism has been
progressively introduced for job execution~\cite{crooks2012multi} but, so far,
% no MPI jobs have been considered for production
HEP applications have not required MPI\mtnote{Addresses Alexei's comment. If
this is still too soft, we can write: ``but HEP applications do not require
MPI.''}. Jobs are supposed to be relatively self-contained, capable of setting
up their own execution environment or having a minimal set of common
dependences.

@@

% Currently, PanDA's execution model is based on five main abstractions: task,
% job, queue, pilot, and event. Both tasks and jobs are assumed to have
% attributes and states and to be queued into a global queue for execution.
% Prioritization and binding of jobs are assumed to depend on the attributes of
% each job. Pilot is used to indicate the abstraction of resource capabilities.
% Each job is thought to be bound to one pilot and executed on the site where
% the pilot has been instantiated.

Currently, PanDA's execution model is based on four main abstractions: task,
job, queue, and pilot. Both tasks and jobs are assumed to have attributes and
states and to be queued into a global queue for execution. Prioritization and
binding of jobs are assumed to depend on the attributes of each job. Pilot is
used to indicate the abstraction of resource capabilities. Each job is thought
to be bound to one pilot and executed on the site where the pilot has been
instantiated.

In PanDA's data model, each
% event
datum refers to the recorded or simulated measurement of a physical
% event
process.
% One or more events
Data can be packaged into files or other containers. As with jobs, data
have both attributes and states, and some of the attributes are shared between
events and jobs. Raw, reconstruction, and simulation data are assumed to be
distributed across multiple storage facilities and managed by the ATLAS
Distributed Data Management (DDM)~\cite{garonne2012atlas}. When necessary,
datasets required by each job are assumed to be replicated over the network,
both for input and output data.

@@

The implementation of PanDA consists of several interconnected subsystems, most
of them built from off-the-shelf and Open Source components. Subsystems
communicate via dedicated API or HTTP messaging, and each subsystem is
implemented by one or more modules. Databases are used to store eventful
entities and entities' description like tasks, jobs and % events
input/output data, and to store information about sites,
resources, logs, and accounting.
